Affective Uplift During Video Game Play: A Naturalistic Case Study

### 2024-02-19 ms.Rmd
Improve environment variable use

knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = 0.618
)
```

>>>>

knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = 0.618
)

# mcmc settings
MAX_CORES <- as.numeric(Sys.getenv("N_CORES"), 4)
N_ITER <- as.numeric(Sys.getenv("N_ITER"), 2000)
options(
  brms.backend = Sys.getenv("BRMS_BACKEND", "rstan"), 
  brms.threads = as.numeric(Sys.getenv("N_THREADS"), 1),
  mc.cores = MAX_CORES
)
```
